DeepFovea++: Reconstruction and Super-Resolution for Natural Foveated Rendered Videos

### 2020-06-23 DeepFovea++ paper/proposal.tex
Add paper (work in progress)

\usepackage[utf8]{inputenc}
\usepackage{caption}
\usepackage{tabularx}
\captionsetup[table]{skip=20pt}
\usepackage{cvpr}
\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{physics}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{subcaption}
\usepackage{bm,color}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{shapes, arrows}
\usepackage{graphics}
\usepackage{pifont}
\pgfplotsset{compat=newest}
\usepackage{blindtext}

@@

% Math styles
\newcommand{\Vector}[1]{\boldsymbol{#1}}
\newcommand{\Matrix}[1]{\boldsymbol{\MakeUppercase{#1}}}
\newcommand{\Tensor}[1]{\boldsymbol{\mathrm{\MakeUppercase{#1}}}}
\newcommand{\Set}[1]{\mathbb{#1}}
\newcommand{\Mean}[1]{\mathbb{E}\left[#1\right]}
\newcommand{\Var}[1]{\mathrm{Var}\left[#1\right]}
\newcommand{\Cov}[1]{\mathrm{Cov}\left[#1\right]}
\newcommand{\Gaussian}[1]{\mathcal{N}\left(#1\right)}

@@

\twocolumn[{%
\renewcommand\twocolumn[1][]{#1}%
\maketitle
\begin{center}
    \centering
    \includegraphics[width=\textwidth]{figures/input.png}\\\vspace{-0.1cm}
    \includegraphics[width=\textwidth]{figures/prediction.png}\\\vspace{-0.1cm}
    \includegraphics[width=\textwidth]{figures/label.png}\\
    \captionof{figure}{Results of our proposed DeepFovea++ technique. The fovea sampled input sequences of low resolution (192 X 256) image frames can be seen on the top. The reconstructed super-resolution (768 X 1024) prediction sequence is shown in the middle, and the corresponding label at the bottom.}
    \label{fig:firstresults}
\end{center}%
}]

\begin{abstract}
Image super-resolution is a well-known problem in the computer vision community. Recent papers extended the problem of super-resolution to videos and showed amazing results. On the other hand deep learning based fovea sampled image reconstruction has drawn some popularity since the DeepFovea publication of Facebook AI. DeepFovea showed outstanding results, however, the proposed reconstruction network was only able to reconstruct relatively low-resolution images of $128\times128$ pixels. We revisit the proposed DeepFovea architecture to perform fovea sampled video reconstruction and super-resolution ($192 \times 256$ $\to$ $768 \times 1024$) at once. Our proposed architecture, DeepFovea++, first reconstructs a given video sequence by a recurrent U-Net architecture, and afterward, the desired super-resolution is learned by deformable convolutions. We tested our DeepFovea++ architecture on the challenging REDS dataset. The code is available at \url{https://github.com/ChristophReich1996/DeepFoveaPP_for_Video_Reconstruction_and_Super_Resolution}.
\end{abstract}

\section{Introduction} % Jonas

\section{Previous Work} % Marius

\section{DeepFovea++ Architecture} % Christoph
The DeepFovea++ reconstruction model is mainly based on two parts. First, a recurrent residual U-Net \cite{unet, deepfovea}, and second, two super-resolution blocks based on deformable convolutions. We train both, the U-Net, and the super-resolution blocks, in an end-to-end setting. The whole reconstruction architecture consists of about 2.3 Mio parameters. We used a relatively small reconstruction model to be able to fit the whole DeepForvea++ framework, consisting of the reconstruction model, a 3d discriminator, and a 3D FFT-discriminator, into GPU memory.

\subsection{Reconstruction model}

\subsection{Discriminator}

\subsection{FFT-Discriminator}

\subsection{Lossfunction}

\subsubsection{Supervised loss}

\subsubsection{Adversarial loss}

\subsubsection{Flow loss}

\section{Experiments} % Christoph

\subsection{REDS Dataset} % Jonas

\subsection{Implementation Details} % Christoph
We implemented the whole DeepFovea++ framework in PyTorch 1.4.0 \cite{pytorch}. Our implementation is based on multiple existing implementations. First, we build our framework on top of the deformable convolution v2 \cite{deformableconv} implementation included in the mmdetection toolbox \cite{mmdetection}. Second, we used the correlation package \cite{flownet2} of Nvidia for implementing the optical flow loss. Furthermore, to estimate the optical flow for the corresponding optical flow loss, we utilized a pre-trained PWC-Net \cite{pwcnet} by Nvidia research. Finally, our main supervised loss function is based on the adaptive robust loss function implementation by Jonathan T. Barron \cite{adaptiveroubustloss}.\\
For optimizing all networks we utilized the Adam optimizer \cite{adam}. For the reconstruction model, we set the learning rate to $3\times 10^{-4}$. The first and second-order running average factors were set 0.1 and 0.95, respectively. In both the 3d discriminator and the 3d FFT-discriminator we set the learning rate to $10^{-4}$. The first and second-order running average factors were set to the same value as for the reconstruction model.\\

TODO: Fovea mask!\\

TODO: Preprcessing\\

We were able to fit one sequence consisting of six rgb frames on one Tesla V100 (16GB). We trained our whole framework for 15 epochs on two GPUs. This results in a batch size of two. This training process took us about two days.

\subsection{Results} % Christoph
For analyzing our framework results we calculated multiple metrics. First, we compute the common $\operatorname{L1}$ metric and the Mean-Squared-Error (MSE, $\operatorname{L2}$). In case for a reconstructed image $\Tensor{I}_{\text{pred}}\in\Set{R}^{c, h, w}$ and the corresponding label $\Tensor{I}_{\text{label}}\in\Set{R}^{c, h, w}$, the $\operatorname{L1}$ and $\operatorname{L2}$ loss is defined as

\begin{align}
    \operatorname{L1} &= \frac{1}{n\times c\times w}\norm{\Tensor{I}_{\text{pred}} - \Tensor{I}_{\text{label}}}_{1}\\
    \operatorname{L2} &= \frac{1}{n\times c\times w}\norm{\Tensor{I}_{\text{pred}} - \Tensor{I}_{\text{label}}}_{2}.
\end{align}

Additionally we compute the Peak-Signal-ToNoise ($\operatorname{PSNR}$) and the, and Structural-Similarity-Image-Metric ($\operatorname{SSIM}$) \cite{ssmi} to evaluate quality of prediction, which are defined as

\begin{align}
    \operatorname{PSNR}&=10 \log_{10},\left(\frac{\max\{\Tensor{I}_{\text{pred}}\}^2}{\operatorname{L2}\left(\Tensor{I}_{\text{pred}}, \Tensor{I}_{\text{label}}\right)} \right)\\
    \operatorname{SSIM}&=\frac{4\Mean{\Tensor{I}_{\text{pred}}}\Mean{\Tensor{I}_{\text{label}}}\Cov{\Tensor{I}_{\text{pred}}, \Tensor{I}_{\text{label}}}}{\left(\Mean{\Tensor{I}_{\text{pred}}}^2 + \Mean{\Tensor{I}_{\text{label}}}^2\right)\left(\Var{\Tensor{I}_{\text{pred}}} + \Var{\Tensor{I}_{\text{label}}}\right)}.
\end{align}

We tested our DeepFovea++ framework with two settings. In the first setting, we reset the recurrent state of the reconstruction model after each video sequence. In the second setting, we preserve the recurrent state over the whole training and validation process. Our tests lead to the following results.\\

TODO: Insert results\\

\section{Conclusion} % All

{\small
    \bibliographystyle{ieee}
    \bibliography{egbib}
}

\section{Appendix}

\begin{figure}[h!]
    \centering
    \includegraphics[width=\columnwidth]{figures/no_rest/input_83_2020-05-06 09_56_21.383738.png}\\\vspace{-0.1cm}
    \includegraphics[width=\columnwidth]{figures/no_rest/prediction_83_2020-05-06 09_56_17.234900.png}\\\vspace{-0.1cm}
    \includegraphics[width=\columnwidth]{figures/no_rest/label_83_2020-05-06 09_56_19.447333.png}\\
    \caption{Results of the first DeepFovea++ setting. The fovea sampled input sequences (192 X 256) on the top. The reconstructed super-resolution (768 X 1024) prediction sequence in the middle, and the corresponding label at the bottom.}
    \label{fig:norestresults1}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=\columnwidth]{figures/rest/input_83_2020-05-04 11_16_57.840082.png}\\\vspace{-0.1cm}
    \includegraphics[width=\columnwidth]{figures/rest/prediction_83_2020-05-04 11_16_53.597074.png}\\\vspace{-0.1cm}
    \includegraphics[width=\columnwidth]{figures/rest/label_83_2020-05-04 11_16_55.895397.png}\\
    \caption{Results of the second DeepFovea++ setting. The fovea sampled input sequences (192 X 256) on the top. The reconstructed super-resolution (768 X 1024) prediction sequence in the middle, and the corresponding label at the bottom.}
    \label{fig:restresults1}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=\columnwidth]{figures/no_rest/input_432_2020-05-06 09_58_44.696719.png}\\\vspace{-0.1cm}
    \includegraphics[width=\columnwidth]{figures/no_rest/prediction_432_2020-05-06 09_58_40.811600.png}\\\vspace{-0.1cm}
    \includegraphics[width=\columnwidth]{figures/no_rest/label_432_2020-05-06 09_58_43.122398.png}\\
    \caption{Results of the first DeepFovea++ setting. The fovea sampled input sequences (192 X 256) on the top. The reconstructed super-resolution (768 X 1024) prediction sequence in the middle, and the corresponding label at the bottom.}
    \label{fig:norestresults2}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=\columnwidth]{figures/rest/input_432_2020-05-04 11_19_22.304534.png}\\\vspace{-0.1cm}
    \includegraphics[width=\columnwidth]{figures/rest/prediction_432_2020-05-04 11_19_18.114088.png}\\\vspace{-0.1cm}
    \includegraphics[width=\columnwidth]{figures/rest/label_432_2020-05-04 11_19_20.713044.png}\\
    \caption{Results of the second DeepFovea++ setting. The fovea sampled input sequences (192 X 256) on the top. The reconstructed super-resolution (768 X 1024) prediction sequence in the middle, and the corresponding label at the bottom.}
    \label{fig:restresults2}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=\columnwidth]{figures/no_rest/input_150_2020-05-06 09_56_53.103463.png}\\\vspace{-0.1cm}
    \includegraphics[width=\columnwidth]{figures/no_rest/prediction_150_2020-05-06 09_56_48.941222.png}\\\vspace{-0.1cm}
    \includegraphics[width=\columnwidth]{figures/no_rest/label_150_2020-05-06 09_56_51.153540.png}\\
    \caption{Results of the first DeepFovea++ setting. The fovea sampled input sequences (192 X 256) on the top. The reconstructed super-resolution (768 X 1024) prediction sequence in the middle, and the corresponding label at the bottom.}
    \label{fig:norestresults3}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=\columnwidth]{figures/rest/input_150_2020-05-04 11_17_29.891315.png}\\\vspace{-0.1cm}
    \includegraphics[width=\columnwidth]{figures/rest/prediction_150_2020-05-04 11_17_25.749898.png}\\\vspace{-0.1cm}
    \includegraphics[width=\columnwidth]{figures/rest/label_150_2020-05-04 11_17_27.920524.png}\\
    \caption{Results of the second DeepFovea++ setting. The fovea sampled input sequences (192 X 256) on the top. The reconstructed super-resolution (768 X 1024) prediction sequence in the middle, and the corresponding label at the bottom.}
    \label{fig:restresults3}
\end{figure}

>>>>

\usepackage[utf8]{inputenc}
\usepackage{caption}
\usepackage{tabularx}
\captionsetup[table]{skip=20pt}
\usepackage{cvpr}
\usepackage{mathptmx}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{amssymb}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{subcaption}
\usepackage{bm,color}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{shapes, arrows}
\usepackage{graphics}
\usepackage{pifont}
\pgfplotsset{compat=newest}
\usepackage{blindtext}

@@

% Math styles
\newcommand{\Vector}[1]{\boldsymbol{#1}}
\newcommand{\Matrix}[1]{\boldsymbol{\MakeUppercase{#1}}}
\newcommand{\Tensor}[1]{\boldsymbol{\mathrm{\MakeUppercase{#1}}}}
\newcommand{\Set}[1]{\mathbb{#1}}
\newcommand{\Mean}[1]{\mathbb{E}\left(#1\right)}
\newcommand{\Var}[1]{\mathrm{Var}\left(#1\right)}
\newcommand{\Cov}[1]{\mathrm{Cov}\left(#1\right)}
\newcommand{\Gaussian}[1]{\mathcal{N}\left(#1\right)}

@@

\twocolumn[{%
\renewcommand\twocolumn[1][]{#1}%
\maketitle
\begin{center}
    \centering
    \includegraphics[width=\textwidth]{figures/input.png}\\\vspace{-0.1cm}
    \includegraphics[width=\textwidth]{figures/prediction.png}\\\vspace{-0.1cm}
    \includegraphics[width=\textwidth]{figures/label.png}\\
    \captionof{figure}{First results of our proposed DeepFovea++ technique. The fovea sampled input sequences of low resolution (192 X 256) image frames can be seen on the top. The reconstructed super-resolution (768 X 1024) prediction sequence is shown in the middle, and the corresponding label at the bottom.}
    \label{fig:results}
\end{center}%
}]

\begin{abstract}
Image super-resolution is a well-known problem in the computer vision community. Recent papers extended the problem of super-resolution to videos and showed amazing results. On the other hand deep learning based fovea sampled image reconstruction has drawn some popularity since the DeepFovea publication of Facebook AI. DeepFovea showed outstanding results, however, the proposed reconstruction network was only able to reconstruct relatively low-resolution images of $128\times128$ pixels. We want to revisit the DeepFovea architecture to perform fovea sampled video reconstruction and super-resolution at once. A first version of out idea is already available at \url{https://github.com/ChristophReich1996/DeepFoveaPP_for_Video_Reconstruction_and_Super_Resolution}.
\end{abstract}

\section{What we want to do?}
We want to combine the problems of super-resolution \cite{valillasuperres} and fovea sampled video reconstruction \cite{kaplanyan2019deepfovea}, to build a more general convolutional neural network (CNN) \cite{cnn} based algorithm. Since to our knowledge, there is currently no algorithm available that can perform these two tasks at once, so we could push the development of CNN algorithms a bit further with our work.

\section{Why project is this important?}
This work could lead, as mentioned earlier, to a more general CNN based algorithm. Furthermore, we possibly could hit the boundary of the capability of CNNs. Which would be also interesting to discover. Besides the theoretical aspects, real-world use-cases like virtual reality could benefit from our work. \cite{kaplanyan2019deepfovea}

\section{Why project is it interesting for you?}
All of us are interested in deep learning for computer vision. In the last semester, we (Marius \& Christoph) already completed the project-lab deep learning in computer vision. So we already have a strong prior knowledge, regarding deep learning in computer vision.
Jonas, on the other hand, has also experience in the field of deep learning in computer vision by building own projects, \href{https://github.com/jonasgrebe/tf-pokemon-generation}{see}.

\section{How we plan to approach the solution?}
We want to build our project on top of the DeepFovea architecture, published by Facebook AI \cite{kaplanyan2019deepfovea}. To achieve video super-resolution we plan to use a deformable convolution approach similar to \cite{deformablesuperres, deformableconv}. We are also interested to apply the adaptive robust loss function by Jonathan Barron \cite{adaptiveroubustloss}. To train, validate and test our architecture we used, in our first experimental tests, the REDS dataset, which included natural video sequences. \cite{REDS}

\section{What we already achieved}
Due to the corona-virus free time, we already managed to build an experimental PyTorch \cite{pytorch} version of our idea. The first tests showed good results as can be seen in figure \ref{fig:results}. We plan the optimize our approach future and to achieve better results and a clean codebase.

{
    \bibliographystyle{ieee}
    \bibliography{egbib}
}
